\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-09 paper/draft.tex
NOAA in eval

\heading{Discussion}
Similar to Unix50~\sx{unix50}, we found that large pipelines enable significant freedom in terms of expressiveness.
A few stages of the original script were expressed in a single \ttt{awk};
% unfortunately, \ttt{awk} is too general to have a single meaningful \todo{parallelizability} signature.
  a simpler (but longer) pipeline that leverages \unix built-ins turns out to be trivially parallelizable.

>>>>

\heading{Discussion}
% 
The speedup of the preprocessing phase of the pipeline is bound by the network and IO costs since \ttt{curl} downloads 82GB of data. However, in the processing phase (which is CPU-bound) the speedup is $12.31\times$, much higher than what would be achieved by parallelizing per loop iteration.
Similar to Unix50~\sx{unix50}, we found that large pipelines enable significant freedom in terms of expressiveness.
% A few stages of the original script were expressed in a single \ttt{awk};
% unfortunately, \ttt{awk} is too general to have a single meaningful \todo{parallelizability} signature.
  % a simpler (but longer) pipeline that leverages \unix built-ins turns out to be trivially parallelizable.
